---
title: "Climate Growth Projection"
author: "Moritz Schwarz and Felix Pretis"
version: "9 June 2020"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("output")) })
editor_options: 
  chunk_output_type: inline
---

**October 2020:**
This script takes the file climate_variables_total.csv and creates the mean-corrected anomaly corrected_anomaly_climatedata.csv.

```{r "setup", message=FALSE}
library(tidyverse)
library(data.table)
library(gets)
library(here)
library(vroom)

library(extrafont)
library(RColorBrewer)
library(Cairo)
library(viridis)

rm(list = ls())
knitr::opts_chunk$set(message = F,echo = T,fig.width = 8)
```


```{r}
maxyear_recur <- 2012

correction <- TRUE
anomaly <- TRUE

# Sanity Check
if(anomaly == FALSE & correction == FALSE){
  stop("Either Correction or Anomaly Creation must be positive - otherwise don't use this script")
  }


country_dataset <- vroom(here("data","use","damage_curve_country_dataset_timetrends_updated02-19.csv"))
```


# Load the climate data
We remove ```altwsdi``` ```altcwd``` ```altcsdi``` ```altcdd")``` because we don't have historical data for them. 

```{r}
climate <- vroom(here("data","out","climate_variables_total.csv")) %>% 
  select(-starts_with("alt")) %>% 
  filter(year<2101) %>% 
  mutate(across(.cols = c(-final_temp, -iso, -model, -rcp, -ensemble,-year),.fns = list(`2` = ~.^2)))
```


```{r}
climate %>% 
  select(-final_temp, -iso, -model, -rcp, -ensemble,-year) %>% 
  names -> correction_vars
```


# Correction
```{r}
if(correction){
  climate %>% 
  filter(year < (maxyear_recur+1)) %>% 
  group_by(iso,final_temp) %>% 
  summarise_at(.vars = vars(-model, -rcp, -ensemble,-year),list(~mean(.,na.rm=T))) %>% 
  ungroup -> future_mean

country_dataset %>% 
  filter(year>2006 & year<(maxyear_recur+1)) %>%
  rename_all(tolower) %>% 
  select(all_of(names(climate %>% select(-model,-rcp,-ensemble,-final_temp,-starts_with("alt"))))) %>% 
  group_by(iso) %>% 
  summarise_at(.vars = vars(-year),list(past=~mean(.,na.rm=T))) %>% 
  ungroup %>% 
  drop_na -> past_mean

future_mean %>% 
  left_join(past_mean,by=c("iso")) -> future_and_past

bind_cols(future_mean %>% select(iso, final_temp),
          future_and_past[, correction_vars] - future_and_past[, paste0(correction_vars, "_past")]) %>% 
  rename_at(.vars = vars(-final_temp,-iso),.funs = ~paste0(.,"_correction"))-> corrected_values

climate %>% 
  left_join(corrected_values,by=c("iso","final_temp")) -> to_be_corrected

bind_cols(climate %>% select(-all_of(correction_vars)),
          to_be_corrected[, correction_vars, with = F] - to_be_corrected[, paste0(correction_vars, "_correction"),
                                                                         with=F]) -> climate_corrected
} else {
  
  climate -> climate_corrected
  
  }
```

# Anomaly
```{r}
if(anomaly){
  country_dataset %>% 
    filter(year>1999&year<2012) %>% 
    select(-year,-contains(c("year_","time","iso_","diff"))) %>% 
    group_by(iso) %>% 
    summarise_all(.funs = ~mean(.,na.rm=T)) %>% 
    rename_all(.funs = ~tolower(.)) %>% 
    select(iso,all_of(correction_vars)) %>% 
    rename_at(.vars = vars(everything(),-iso),~paste0(.,"_anomaly")) -> base_scenario_mean
  
climate_corrected %>% 
  left_join(base_scenario_mean,by="iso")-> anomaly_to_be_created

climate_corrected %>% 
  select(model,rcp,ensemble,final_temp,iso,year) %>% 
  bind_cols(.,anomaly_to_be_created[,correction_vars, with=F] - anomaly_to_be_created[,paste0(correction_vars,"_anomaly"), with=F]) -> climate_ready
  
} else {
  climate_corrected -> climate_ready
}

```


# Save
```{r}
if(correction&anomaly){write_csv(climate_ready, path = here("data","temp","corrected_anomaly_climatedata.csv"))}
if(!correction&anomaly){write_csv(climate_ready, path = here("data","temp","anomaly_climatedata.csv"))}
if(correction&!anomaly){write_csv(climate_ready, path = here("data","temp","corrected_climatedata.csv"))}
```


# Plotting to illustrate corrections
## Choosing final temperatures to plot
```{r, echo=FALSE}
climate_corrected %>% 
  distinct(final_temp) %>% 
  pull -> plotting_temp

# Selecting the second temperature, the 25%, 50% and 75% as well as the penultimate estimate
plotting_temp <- plotting_temp[c(2,length(plotting_temp)/4,
                                 length(plotting_temp)/2,
                                 length(plotting_temp)*3/4,
                                 length(plotting_temp)-1)]  
```


## Time Series to 2100
### Original CMIP5
```{r, echo=FALSE}
climate %>% 
  filter(iso %in% c("USA","CHN","AUT"),
         final_temp %in% plotting_temp, 
         year < 2101) %>% 
  mutate(final_temp = round(final_temp,1)) %>% 
  
  ggplot(aes(x=year,y=temp,group=final_temp,color=iso)) + 
  
  geom_line() +
  geom_hline(aes(yintercept = 0))+
  
  facet_grid(iso~final_temp,labeller = labeller(.cols = function(x){paste0(x,"°C Anomaly")})) + 
  
  scale_color_viridis_d()+
  
  labs(y="Temperature in °C",title = "Original CMIP5 Data",x="")+

  theme(legend.position = "none", 
        panel.grid.major = element_line(colour = "grey",size = 0.5),
        panel.background = element_blank(),
        text = element_text(family = "Georgia",size = 15)) 
  
```

### Corrected

```{r, echo=FALSE}
climate_corrected %>% 
  filter(iso %in% c("USA","CHN","AUT"),
         final_temp %in% plotting_temp) %>% 
  mutate(final_temp = round(final_temp,1)) %>% 
  
  ggplot(aes(x=year,y=temp,group=final_temp,color=iso)) + 
  
  geom_line() +
  geom_hline(aes(yintercept = 0))+
  
  facet_grid(iso~final_temp,labeller = labeller(.cols = function(x){paste0(x,"°C Anomaly")})) + 
  
  scale_color_viridis_d()+
  
  labs(y="Temperature in °C",title = "Mean Corrected CMIP5 Data",x="")+

  theme(legend.position = "none", 
        panel.grid.major = element_line(colour = "grey",size = 0.5),
        panel.background = element_blank(),
        text = element_text(family = "Georgia",size = 15)) 
```

### Climate Ready
```{r, echo=FALSE}
climate_ready %>% 
  filter(iso %in% c("USA","CHN","AUT"),
         final_temp %in% plotting_temp) %>% 
  mutate(final_temp = round(final_temp,1)) %>% 
  
  ggplot(aes(x=year,y=temp,group=final_temp,color=iso)) + 
  
  geom_line() +
  geom_hline(aes(yintercept = 0))+
  
  facet_grid(iso~final_temp,labeller = labeller(.cols = function(x){paste0(x,"°C Anomaly")})) + 
  
  scale_color_viridis_d()+
  
  labs(y="Temperature in °C",title = "Mean Corrected CMIP5 Data",x="")+

  theme(legend.position = "none", 
        panel.grid.major = element_line(colour = "grey",size = 0.5),
        panel.background = element_blank(),
        text = element_text(family = "Georgia",size = 15))
```



## Checking corrections to 2020
### Original CMIP5
```{r, echo=FALSE} 
climate %>% 
  filter(iso %in% c("USA","CHN","AUT"),
         final_temp %in% plotting_temp,
         year < 2021) %>% 
  mutate(final_temp = round(final_temp,1)) %>% 
  
  ggplot(aes(x=year,y=temp,group=final_temp,color=final_temp)) + 
  
  geom_line() +
  geom_hline(aes(yintercept = 0))+
  
  facet_wrap(~iso,nrow=1)+
  #facet_grid(iso~final_temp,labeller = labeller(.cols = function(x){paste0(x,"°C Anomaly")})) + 
  
  scale_color_viridis_c()+
  
  labs(y="Temperature in °C",title = "Original CMIP5 Data",x="")+

  theme(panel.grid.major = element_line(colour = "grey",size = 0.5),
        panel.background = element_blank(),
        text = element_text(family = "Georgia",size = 15))
  
```

### Climate Corrected
```{r, echo=FALSE}
climate_corrected %>% 
  filter(iso %in% c("USA","CHN","AUT"),
         final_temp %in% plotting_temp,
         year < 2021) %>% 
  mutate(final_temp = round(final_temp,1)) %>% 
  
  ggplot(aes(x=year,y=temp,group=final_temp,color=final_temp)) + 
  
  geom_line() +
  geom_hline(aes(yintercept = 0))+
  
  facet_wrap(~iso,nrow=1)+
  #facet_grid(iso~final_temp,labeller = labeller(.cols = function(x){paste0(x,"°C Anomaly")})) + 
  
  scale_color_viridis_c()+
  
  labs(y="Temperature in °C",title = "Mean Corrected CMIP5 Data",x="")+

  theme(panel.grid.major = element_line(colour = "grey",size = 0.5),
        panel.background = element_blank(),
        text = element_text(family = "Georgia",size = 15))
  
```

### Climate Ready
```{r, echo=FALSE}
climate_ready %>% 
  filter(iso %in% c("USA","CHN","AUT"),
         final_temp %in% plotting_temp,
         year < 2021) %>% 
  mutate(final_temp = round(final_temp,1)) %>% 
  
  ggplot(aes(x=year,y=temp,group=final_temp,color=final_temp)) + 
  
  geom_line() +
  geom_hline(aes(yintercept = 0))+
  
  facet_wrap(~iso,nrow=1)+
  #facet_grid(iso~final_temp,labeller = labeller(.cols = function(x){paste0(x,"°C Anomaly")})) + 
  
  scale_color_viridis_c()+
  
  labs(y="Temperature in °C",title = "Mean Corrected CMIP5 Data",x="")+

  theme(panel.grid.major = element_line(colour = "grey",size = 0.5),
        panel.background = element_blank(),
        text = element_text(family = "Georgia",size = 15))
  
```




