---
title: "Model Estimation"
author: "Moritz Schwarz and Felix Pretis"
version: "2 June 2020"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("output")) })
---

**October 2020:**
This script creates the model .RData files and needs the file selection_matrix.csv as input.
For gets, it also needs getsm_nolag_nointcp_0.05_stage2.RData as input. 
For BMS, it also needs bm1.2.RData, bm2.2.RData, bm3.2.RData, and bm4.2.RData as input.
For LASSO, it also needs two_stage2_x_lass_cv_nolag_nointcp.RData as input.

```{r "setup", message=FALSE}
library(tidyverse)
library(data.table)
library(gets)
library(here)


# library(extrafont)
# library(RColorBrewer)
# library(Cairo)
# library(viridis)

rm(list = ls())
select <- dplyr::select
knitr::opts_chunk$set(message = F,echo = T,fig.width = 8, comment=NA)
```


This starts out with an estimated GETS file and then adds interactions. 
```{r}
load_getsm <- TRUE
selection_matrix <- fread(here("data","temp","selection_matrix.csv"))
```

# BHM
```{r}
BHM_model <- lm(formula = dep_var ~ .-1,
                    data = selection_matrix %>% 
                  select(dep_var,L1.diff.ln_gdp_cap,temp,temp_2,prcp, prcp_2,contains(c("year_","iis","iso_","time_"))))

#summary(BHM_model)
```


# GETS
For GETS, we will load an existing file.
```{r}
#load all the relevant files 
if(load_getsm){load(here("data","temp","getsm_nolag_nointcp_0.05_stage2.RData")); selection=getsm_selection_stage_2}
```

Select the right variables and define the interactions:
```{r}
selection_matrix %>% 
  select(all_of(selection %>% coef %>% names)) %>% 
  select(-L1.diff.ln_gdp_cap,-contains(c("time","year","iso","iis"))) %>% 
  names -> selected_climate_variables


selection_matrix %>% 
  select(iso,year,gdp_cap,dep_var,all_of(selection %>% coef %>% names)) %>% 
  mutate_at(.vars = vars(all_of(selected_climate_variables)),
            .funs = list(int = ~.*selection_matrix$gdp_cap)) %>% 
  
  # Moving the interacted terms forward
  select(iso, year, gdp_cap, dep_var, L1.diff.ln_gdp_cap, all_of(selected_climate_variables), 
         ends_with("int"), everything()) -> df
```


Recreate the GETS result
```{r}
# Uncomment to compare
# selection$coefficients

standard_model<- lm(formula = dep_var ~ .-1, df %>% select(-iso,-year,-gdp_cap, -ends_with("int")))
```

Introduce Interaction for all variables
```{r}
#formula <- as.formula(paste0("dep_var ~ ",paste0("gdp_cap:",selected_climate_variables,collapse = " + ")," + .-1"))

interaction_model_all <- lm(formula = dep_var ~ . -1, df %>% select(-iso,-year, -gdp_cap))
```

Interaction Model gets selection
```{r, message=TRUE}
arx(y=df$dep_var,
    mxreg = df %>% select(-iso,-year, -gdp_cap, -dep_var) %>% as.matrix,
    mc=F) %>% 
  getsm(
    object = .,
    t.pval = 0.05,
    ar.LjungB = NULL,
    arch.LjungB = NULL,
    normality.JarqueB = NULL,
    keep = which(!names(df %>% select(-iso,-year, -gdp_cap, -dep_var)) %in% paste0(selected_climate_variables,"_int"))
  ) -> interaction_model_gets

interaction_model_selected <- lm(formula = dep_var ~ . -1, data = df %>% select(dep_var, all_of(interaction_model_gets %>% coef %>% names)))
```

## Log Interaction
```{r, message=TRUE,eval=TRUE}
selection_matrix %>% 
  select(iso,year,gdp_cap,dep_var,all_of(selection %>% coef %>% names)) %>% 
  mutate_at(.vars = vars(all_of(selected_climate_variables)),
            .funs = list(int = ~.*log(selection_matrix$gdp_cap))) %>% 
  
  # Moving the interacted terms forward
  select(iso, year, gdp_cap, dep_var, 
         L1.diff.ln_gdp_cap, all_of(selected_climate_variables), 
         ends_with("int"), everything()) -> df

interaction_model_all_log <- lm(formula = dep_var ~ . -1, df %>% select(-iso,-year, -gdp_cap))
```

## Log Interaction Selection
```{r, message=TRUE,eval=TRUE}
arx(y=df$dep_var,
    mxreg = df %>% select(-iso,-year, -gdp_cap, -dep_var) %>% as.matrix,
    mc=F) %>% 
  getsm(
    object = .,
    t.pval = 0.05,
    ar.LjungB = NULL,
    arch.LjungB = NULL,
    normality.JarqueB = NULL,
    keep = which(!names(df %>% select(-iso,-year, -gdp_cap, -dep_var)) %in% paste0(selected_climate_variables,"_int"))
  ) -> interaction_model_gets

interaction_model_selected_log <- lm(formula = dep_var ~ . -1, data = df %>% select(dep_var, all_of(interaction_model_gets %>% coef %>% names)))
```

## First

```{r}
selection_matrix %>% 
  select(year,dep_var,all_of(selection %>% coef %>% names)) %>% 
  filter(year %in% c(min(year):(min(year)+30))) %>% 
  select(-year) -> first_df
  

first_model <- lm(dep_var ~ .-1,first_df)
drop <- names(coefficients(first_model))[which(is.na(coefficients(first_model)))] #checks which coefficients are na in the above regression

first_model <- lm(dep_var ~ .-1,first_df %>% select(-all_of(drop)))
```


## Last
```{r}
selection_matrix %>% 
  select(year,dep_var,all_of(selection %>% coef %>% names)) %>% 
  filter(year %in% c((max(year)-30):(max(year)))) %>% 
  select(-year) -> last_df
  
last_model <- lm(dep_var ~ .-1,last_df)
drop <- names(coefficients(last_model))[which(is.na(coefficients(last_model)))] #checks which coefficients are na in the
last_model <- lm(dep_var ~ .-1,last_df %>% select(-all_of(drop)))
```


# LASSO
```{r}
load_lasso <- TRUE
```

## Standard
```{r}
if(load_lasso){
  load(here("data/temp/two_stage2_x_lass_cv_nolag_nointcp.RData"))
  x_lass_cv = x_lass_cv_2}

lasso_formula <- as.formula(paste0("dep_var ~ ",paste0(x_lass_cv,collapse = " + "),"-1"))

lasso_standard_model <- lm(formula = lasso_formula, selection_matrix)

```

## Prepare interaction
```{r}
selection_matrix %>% 
  select(all_of(x_lass_cv)) %>% 
  select(-L1.diff.ln_gdp_cap,-contains(c("time","year","iso","iis"))) %>% 
  names -> selected_climate_variables


selection_matrix %>% 
  select(iso,year,gdp_cap,dep_var,all_of(x_lass_cv)) %>% 
  mutate_at(.vars = vars(all_of(selected_climate_variables)),
            .funs = list(int = ~.*selection_matrix$gdp_cap)) %>% 
  
  # Moving the interacted terms forward
  select(iso, year, gdp_cap, dep_var, L1.diff.ln_gdp_cap, all_of(selected_climate_variables), 
         ends_with("int"), everything()) -> df
```


## Non-Log Interaction (not used)
Introduce Interaction for all variables
```{r, eval=F}
#formula <- as.formula(paste0("dep_var ~ ",paste0("gdp_cap:",selected_climate_variables,collapse = " + ")," + .-1"))

lasso_interaction_model_all <- lm(formula = dep_var ~ . -1, df %>% select(-iso,-year, -gdp_cap))
```

Interaction Model gets selection
```{r, message=TRUE, eval=F}
arx(y=df$dep_var,
    mxreg = df %>% select(-iso,-year, -gdp_cap, -dep_var) %>% as.matrix,
    mc=F) %>% 
  getsm(
    object = .,
    t.pval = 0.05,
    ar.LjungB = NULL,
    arch.LjungB = NULL,
    normality.JarqueB = NULL,
    keep = which(!names(df %>% select(-iso,-year, -gdp_cap, -dep_var)) %in% paste0(selected_climate_variables,"_int"))
  ) -> interaction_model_lasso

lasso_interaction_model_selected <- lm(formula = dep_var ~ . -1, data = df %>% select(dep_var, all_of(interaction_model_lasso %>% coef %>% names)))
```

## Log Interaction
```{r, message=TRUE,eval=TRUE}
selection_matrix %>% 
  select(iso,year,gdp_cap,dep_var,all_of(x_lass_cv)) %>% 
  mutate_at(.vars = vars(all_of(selected_climate_variables)),
            .funs = list(int = ~.*log(selection_matrix$gdp_cap))) %>% 
  
  # Moving the interacted terms forward
  select(iso, year, gdp_cap, dep_var, 
         L1.diff.ln_gdp_cap, all_of(selected_climate_variables), 
         ends_with("int"), everything()) -> df

lasso_interaction_model_all_log <- lm(formula = dep_var ~ . -1, df %>% select(-iso,-year, -gdp_cap))
```

## Log Interaction Selection
```{r, message=TRUE,eval=TRUE}
arx(y=df$dep_var,
    mxreg = df %>% select(-iso,-year, -gdp_cap, -dep_var) %>% as.matrix,
    mc=F) %>% 
  getsm(
    object = .,
    t.pval = 0.05,
    ar.LjungB = NULL,
    arch.LjungB = NULL,
    normality.JarqueB = NULL,
    keep = which(!names(df %>% select(-iso,-year, -gdp_cap, -dep_var)) %in% paste0(selected_climate_variables,"_int"))
  ) -> interaction_model_lasso

lasso_interaction_model_selected_log <- lm(formula = dep_var ~ . -1, data = df %>% select(dep_var, all_of(interaction_model_lasso %>% coef %>% names)))
```

## First

```{r}
selection_matrix %>% 
  select(year,dep_var,all_of(x_lass_cv)) %>% 
  filter(year %in% c(min(year):(min(year)+30))) %>% 
  select(-year) -> first_df
  

lasso_first_model <- lm(dep_var ~ .-1,first_df)
drop <- names(coefficients(lasso_first_model))[which(is.na(coefficients(lasso_first_model)))] #checks which coefficients are na in the above regression

lasso_first_model <- lm(dep_var ~ .-1,first_df %>% select(-all_of(drop)))
```


## Last
```{r}
selection_matrix %>% 
  select(year,dep_var,all_of(x_lass_cv)) %>% 
  filter(year %in% c((max(year)-30):(max(year)))) %>% 
  select(-year) -> last_df
  
lasso_last_model <- lm(dep_var ~ .-1,last_df)
drop <- names(coefficients(lasso_last_model))[which(is.na(coefficients(lasso_last_model)))] #checks which coefficients are na in the
lasso_last_model <- lm(dep_var ~ .-1,last_df %>% select(-all_of(drop)))

```











# Bayesian Model Selection

# Display Models
```{r, results="asis", echo=FALSE,out.width=10, eval=F}

load(here("data","temp","standard_gets_model.RData"))
load(here("data","temp","standard_LASSO_model.RData"))
load(here("data","temp","standard_gets_model.RData"))
load(here("data","temp","standard_gets_model.RData"))


load(here("data","temp","first_gets_model.RData"))
load(here("data","temp","last_gets_model.RData"))

load(here("data","temp","interaction_model_all.RData"))
load(here("data","temp","interaction_model_selected.RData"))
load(here("data","temp","log_interaction_model_all.RData"))
load(here("data","temp","log_interaction_model_selected.RData"))

load(here("data","temp","standard_lasso_model.RData"))
load(here("data","temp","BHM_model.RData"))



stargazer::stargazer(standard_model,
                     first_model,
                     last_model,
                     interaction_model_all, 
                     interaction_model_selected, 
                     interaction_model_all_log,
                     interaction_model_selected_log,
                     lasso_standard_model,
                     BHM_model,
                     type = "text",
                     digits = 6,
                     column.labels = c("Standard","Interaction All","Interaction Selected",
                                       "Interaction All Log","Interaction Selected Log"),
                     omit = c("iis|time|year|iso"))
```





# Save Models
```{r}
save(standard_model,file = here("data","temp","standard_gets_model.RData"))
save(first_model,file = here("data","temp","first_gets_model.RData"))
save(last_model,file = here("data","temp","last_gets_model.RData"))

save(interaction_model_all,file = here("data","temp","interaction_model_all.RData"))
save(interaction_model_selected,file = here("data","temp","interaction_model_selected.RData"))
save(interaction_model_all_log,file = here("data","temp","log_interaction_model_all.RData"))
save(interaction_model_selected_log,file = here("data","temp","log_interaction_model_selected.RData"))


save(lasso_standard_model,file = here("data","temp","standard_lasso_model.RData"))
save(lasso_interaction_model_all_log,file = here("data","temp","lasso_log_interaction_model_all.RData"))
save(lasso_interaction_model_selected_log,file = here("data","temp","lasso_log_interaction_model_selected.RData"))
save(lasso_first_model,file = here("data","temp","first_lasso_model.RData"))
save(lasso_last_model,file = here("data","temp","last_lasso_model.RData"))



save(BHM_model,file = here("data","temp","BHM_model.RData"))
```




# BMS Models

1. uniform
2. fixed
3. pip
4. random

```{r}
library(BMS)
```

## Load selection matrix
```{r}
selection_matrix <- read_csv(here("data","temp","selection_matrix.csv"))
```


### Create Coefficient Dataframe

```{r}
load(here("data","use","BMS","two-step","bm1.2.RData"))
load(here("data","use","BMS","two-step","bm2.2.RData"))
load(here("data","use","BMS","two-step","bm3.2.RData"))
load(here("data","use","BMS","two-step","bm4.2.RData"))

for(i in 1:4){
  if(i==1){relevant_bm <- bm1.2}
  if(i==2){relevant_bm <- bm2.2}
  if(i==3){relevant_bm <- bm3.2}
  if(i==4){relevant_bm <- bm4.2}
  
  relevant_bm %>% 
    beta.draws.bma() %>% 
    data.frame(variable = row.names(.),.) %>% 
    as_tibble() %>% 
    setNames(c("variable",paste0("m_",1:(ncol(.)-1)))) -> bm_coefs
  
  relevant_bm %>% 
    topmodels.bma() %>% 
    data.frame(variable = row.names(.),.) %>% 
    as_tibble() %>% 
    setNames(c("variable",paste0("m_",1:(ncol(.)-1)))) -> topmod_bm
  
  
  take_BMS_coef <- FALSE
  if (take_BMS_coef) {
    topmod_bm <- topmod_bm[c((nrow(topmod_bm) - 1):nrow(topmod_bm)), ] # get the two last rows
    bm_coefs <- rbind(bm_coefs, topmod_bm) # attach them to the beta.draws data.frame
  }
  
  bm_overall <- tibble()
  for(k in 1:(ncol(bm_coefs)-1)){
    print(k)
    if(!take_BMS_coef){
      selection_matrix %>% 
        select(all_of(c("dep_var",topmod_bm %>% 
                          select(variable,all_of(paste0("m_",k))) %>% 
                          filter(!!as.symbol(paste0("m_",k)) == 1) %>% # filter out all variables that are included in the model
                          filter(!variable %in% c("PMP (Exact)","PMP (MCMC)")) %>% 
                          pull(variable)))) -> mat_bms
      
      
      arx(y = mat_bms %>% select(dep_var) %>% pull,
          mxreg =  mat_bms %>% select(-dep_var) %>% as.matrix, 
          mc=F) %>% 
        
        coef %>% 
        
        data.frame(variable = names(.),coef = ., row.names = NULL) %>% 
        
        filter(!grepl("iis|L1.diff.ln_gdp_cap|iso_|year_|time_",variable))  %>% 
        
        mutate(model = k,
               PMP_Exact = topmod_bm %>% select(variable, all_of(paste0("m_", k))) %>% filter(variable == "PMP (Exact)") %>% pull,
               PMP_MCMC = topmod_bm %>% select(variable, all_of(paste0("m_", k))) %>% filter(variable == "PMP (MCMC)") %>% pull) %>% 
        relocate(model) %>% 
        
        bind_rows(bm_overall,.) -> bm_overall
    }
  }
  write_csv(bm_overall,here("data","temp",paste0("BMS_Model_",i,"_coefficients.csv")))
}

```