---
title: "Mueller et al Projection"
subtitle: "First and Last Adaptation"
author: "Moritz Schwarz and Felix Pretis"
version: "October 2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("output")) })
---

```{r,purl = FALSE}
knitr::opts_chunk$set(message = F,echo = T,fig.width = 10)
```


```{r "setup", message=FALSE}
library(tidyverse)
library(data.table)
library(gets)
library(here)
library(vroom)
library(MASS)

library(extrafont)
library(RColorBrewer)
library(Cairo)
library(viridis)


rm(list = ls())
select <- dplyr::select
```


<!-- **To create Server Script: Save first then** -->
<!-- ```{r,eval= TRUE, purl = FALSE} -->
<!-- knitr::purl(here("code","3c. Mueller Effect Projections Adaptation - First and Last.Rmd"),output = here("code","3c. Server_Mueller_Adaptation_FirstLast.R")) -->
<!-- ``` -->

# Load Mueller at el data
```{r}
mueller <- readxl::read_excel(here("data","raw","Predictive_ Distributions_by_Country.xlsx"),
                              skip = 6,col_names = c("iso","empty1","value_2017","empty2","fifty_mean","fifty_0.05",
                                                     "fifty_0.16","fifty_0.5","fifty_0.84","fifty_0.95", "empty3","hundred_mean","hundred_0.05",
                                                     "hundred_0.16","hundred_0.5","hundred_0.84","hundred_0.95", "empty4","unknown")) %>% select(-contains("empty"))

mueller_mean <- mueller %>% 
  select(iso, value_2017, contains("mean"))

mueller_mean %>% 
  mutate(year = 2017,
         gdp_cap = exp(value_2017),
         gdp_cap_fifty = gdp_cap,
         gdp_cap_fifty_climate = gdp_cap_fifty,
         gdp_cap_hundred = gdp_cap,
         gdp_cap_hundred_climate = gdp_cap_hundred,
         fifty_mean = (fifty_mean/100)+1,
         hundred_mean = (hundred_mean/100)+1,
         value_2017 = NULL,
         gdp_cap = NULL) %>% 
  select(iso,year,gdp_cap_fifty, gdp_cap_hundred,everything()) -> mueller_df
```

## Prepare the Max GDP Restriction
Here we identify the 2017 Level of GDP that will act as our restriction.
```{r}
base_gdp <- mueller_df %>% filter(year==2017) %>% 
  select(iso,gdp_cap_fifty,gdp_cap_hundred) %>% 
  rename(base_fifty = gdp_cap_fifty,
         base_hundred = gdp_cap_hundred)

restrict_max_gdp_int = TRUE
```


```{r}
coefsamples <- 100
```

# First GETS
## Load coefficients
```{r}
load(here("data","temp","first_gets_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = first_model %>% coef(), Sigma = first_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  first_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>% 
  pivot_longer(cols = everything()) %>% 
  ggplot(aes(x=value)) + 
  geom_histogram() + 
  facet_wrap(~name,scales = "free") + 
  geom_vline(data = first_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```


## Collect Relevant Information

```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected

```

## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- mueller_df %>% 
    select(-contains("fifty")) %>% 
    filter(year==2017) %>% 
    left_join(effect_standard %>% 
                filter(year == 2017) %>% 
                select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2018:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,contains("hundred")) %>% 
      # this step: 
      left_join(effect_standard %>% 
                  filter(year == i-1) %>% 
                  mutate(realisation = v) %>% 
                  select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      mutate(#gdp_cap_fifty = gdp_cap_fifty*fifty_mean,
        gdp_cap_hundred = gdp_cap_hundred*hundred_mean,
        #gdp_cap_fifty_climate = gdp_cap_fifty_climate*(fifty_mean + total_climate_effect),
        gdp_cap_hundred_climate = gdp_cap_hundred_climate*(hundred_mean + total_climate_effect),
        year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
  save(done,file = here("data","temp","projections",paste0("full_Mueller_firstgets_",v,".RData")))
  rm(done,i)
}
```



# Last GETS
## Load coefficients
```{r}
load(here("data","temp","last_gets_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = last_model %>% coef(), Sigma = last_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  last_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>% 
  pivot_longer(cols = everything()) %>% 
  ggplot(aes(x=value)) + 
  geom_histogram() + 
  facet_wrap(~name,scales = "free") + 
  geom_vline(data = last_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```


## Collect Relevant Information

```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected

```

## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- mueller_df %>% 
    select(-contains("fifty")) %>% 
    filter(year==2017) %>% 
    left_join(effect_standard %>% 
                filter(year == 2017) %>% 
                select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2018:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,contains("hundred")) %>% 
      # this step: 
      left_join(effect_standard %>% 
                  filter(year == i-1) %>% 
                  mutate(realisation = v) %>% 
                  select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      mutate(#gdp_cap_fifty = gdp_cap_fifty*fifty_mean,
        gdp_cap_hundred = gdp_cap_hundred*hundred_mean,
        #gdp_cap_fifty_climate = gdp_cap_fifty_climate*(fifty_mean + total_climate_effect),
        gdp_cap_hundred_climate = gdp_cap_hundred_climate*(hundred_mean + total_climate_effect),
        year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
  save(done,file = here("data","temp","projections",paste0("full_Mueller_lastgets_",v,".RData")))
  rm(done,i)
}
```



# First LASSO
## Load coefficients
```{r}
load(here("data","temp","first_lasso_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = lasso_first_model %>% coef(), Sigma = lasso_first_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  lasso_first_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r, eval= FALSE, purl = FALSE}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>% 
  pivot_longer(cols = everything()) %>% 
  ggplot(aes(x=value)) + 
  geom_histogram() + 
  facet_wrap(~name,scales = "free") + 
  geom_vline(data = first_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```


## Collect Relevant Information

```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected

```

## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- mueller_df %>% 
    select(-contains("fifty")) %>% 
    filter(year==2017) %>% 
    left_join(effect_standard %>% 
                filter(year == 2017) %>% 
                select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2018:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,contains("hundred")) %>% 
      # this step: 
      left_join(effect_standard %>% 
                  filter(year == i-1) %>% 
                  mutate(realisation = v) %>% 
                  select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      mutate(#gdp_cap_fifty = gdp_cap_fifty*fifty_mean,
        gdp_cap_hundred = gdp_cap_hundred*hundred_mean,
        #gdp_cap_fifty_climate = gdp_cap_fifty_climate*(fifty_mean + total_climate_effect),
        gdp_cap_hundred_climate = gdp_cap_hundred_climate*(hundred_mean + total_climate_effect),
        year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
  
  save(done,file = here("data","temp","projections",paste0("full_Mueller_firstlasso_",v,".RData")))
  rm(done,i)
}
```



# Last LASSO
## Load coefficients
```{r}
load(here("data","temp","last_lasso_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = lasso_last_model %>% coef(), Sigma = lasso_last_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  lasso_last_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r, eval= FALSE, purl = FALSE}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>% 
  pivot_longer(cols = everything()) %>% 
  ggplot(aes(x=value)) + 
  geom_histogram() + 
  facet_wrap(~name,scales = "free") + 
  geom_vline(data = last_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```


## Collect Relevant Information

```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected

```

## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- mueller_df %>% 
    select(-contains("fifty")) %>% 
    filter(year==2017) %>% 
    left_join(effect_standard %>% 
                filter(year == 2017) %>% 
                select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2018:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,contains("hundred")) %>% 
      # this step: 
      left_join(effect_standard %>% 
                  filter(year == i-1) %>% 
                  mutate(realisation = v) %>% 
                  select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      mutate(#gdp_cap_fifty = gdp_cap_fifty*fifty_mean,
        gdp_cap_hundred = gdp_cap_hundred*hundred_mean,
        #gdp_cap_fifty_climate = gdp_cap_fifty_climate*(fifty_mean + total_climate_effect),
        gdp_cap_hundred_climate = gdp_cap_hundred_climate*(hundred_mean + total_climate_effect),
        year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
  save(done,file = here("data","temp","projections",paste0("full_Mueller_lastlasso_",v,".RData")))
  rm(done,i)
}
```



