---
title: "SSP Projection"
subtitle: "Standard"
author: "Moritz Schwarz and Felix Pretis"
version: "October 2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("output")) })
---

```{r,purl = FALSE}
knitr::opts_chunk$set(message = F,echo = T,fig.width = 10)
```


```{r "setup", message=FALSE}
library(tidyverse)
library(data.table)
library(gets)
library(here)
library(vroom)
library(MASS)

library(extrafont)
library(RColorBrewer)
library(Cairo)
library(viridis)


rm(list = ls())
select <- dplyr::select
```


<!-- **To create Server Script: Save first then** -->
<!-- ```{r,eval= TRUE, purl = FALSE} -->
<!-- knitr::purl(here("code","4a. SSP Effect Projections - standard.Rmd"),output = here("code","4a. Server_SSP.R")) -->
<!-- ``` -->



# SSP
## Process 
```{r}
SSP_wide <- vroom(file=here("data","raw","SspDb_country_data_2013-06-12.csv"))

SSP_wide %>% 
  filter(MODEL == "OECD Env-Growth") %>% 
  filter(VARIABLE %in% c("Population","GDP|PPP")) %>% 
  pivot_longer(cols = -c(MODEL,SCENARIO,REGION,VARIABLE,UNIT),names_to = "YEAR") %>% 
  mutate(YEAR = YEAR %>% as.character %>% as.integer) %>% 
  pivot_wider(id_cols = c(MODEL,SCENARIO,REGION,YEAR),names_from = VARIABLE) %>% 
  
  mutate(GDP = `GDP|PPP`*1000000000,
         `GDP|PPP`=NULL,
         POPULATION = `Population`*1000000,
         `Population`=NULL,
         GDP_pc = GDP/POPULATION,
         MODEL = NULL,
         SCENARIO = gsub("_v9_130325","",SCENARIO)) %>% 
  
  filter(!YEAR == 2000) %>% 
  drop_na -> ssp
```

## Interpolate SSPs using a simple spline
```{r}
ssp %>% 
  select(REGION) %>% 
  unique %>% 
  slice(rep(1:n(), each = 90)) %>%
  group_by(REGION) %>% 
  mutate(YEAR = 1:90) %>% 
  ungroup() %>% 
  mutate(YEAR = YEAR + 2009) %>% 
  full_join(ssp %>% 
              select(-GDP,-POPULATION) %>% 
              filter(YEAR >2005) %>% 
              pivot_wider(id_cols = c(REGION,YEAR),values_from = "GDP_pc",names_from = "SCENARIO"),by=c("REGION","YEAR")) %>% 
  group_by(REGION) %>% 
  mutate(SSP1 = zoo::na.spline(SSP1,YEAR),
         SSP2 = zoo::na.spline(SSP2,YEAR),
         SSP3 = zoo::na.spline(SSP3,YEAR),
         SSP4 = zoo::na.spline(SSP4,YEAR),
         SSP5 = zoo::na.spline(SSP5,YEAR)) %>% 
  ungroup %>% 
  rename(iso = REGION,
         year = YEAR) -> ssp

#write.csv(ssp,"ssp/ssp_interpolated.csv",row.names = F)
```

```{r}
ssp %>% 
  group_by(iso) %>% 
  mutate(across(.cols = starts_with("SSP"),.fns = ~./lag(.))) %>% 
  ungroup %>% 
  drop_na %>% 
  rename_with(.cols = starts_with("SSP"),.fn = ~paste0(.,"_g"))-> ssp_growth
```

Prepare the SSP dataframe so that it has: 1) the SSP growth rates 2) the SSP Climate Placeholders starting in 2011
```{r}
ssp_growth %>% 
  #left_join(ssp,by=c("iso","year")) %>% 
  left_join(ssp %>% 
              filter(year == 2011) %>% 
              rename_with(.cols = starts_with("SSP"),.fn = ~paste0(.,"_clim")),by=c("iso","year")) -> ssp_ready
```



```{r}
coefsamples <- 100
```

# GETS
## Load coefficients
```{r}
load(here("data","temp","standard_gets_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = standard_model %>% coef(), Sigma = standard_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  standard_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r, eval= FALSE, purl = FALSE}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>%
  pivot_longer(cols = everything()) %>%
  ggplot(aes(x=value)) +
  geom_histogram() +
  facet_wrap(~name,scales = "free") +
  geom_vline(data = standard_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>%
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```



## Collect Relevant Information
```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected
```


## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- ssp_ready %>% 
    filter(year==2011) %>% 
    inner_join(effect_standard %>% 
                 filter(year == 2011) %>% 
                 select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2012:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,ends_with("_clim")) %>% #contains(SSP_scenarios_running)
      
      inner_join(ssp_ready %>% 
                   select(-ends_with("_clim")) %>% 
                   filter(year == i-1), by = c("iso","year")) %>% 
      # this step: 
      inner_join(effect_standard %>% 
                   filter(year == i-1) %>% 
                   mutate(realisation = v) %>% 
                   select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      
      mutate(SSP1_clim = SSP1_clim*(SSP1_g + total_climate_effect),
             SSP2_clim = SSP2_clim*(SSP2_g + total_climate_effect),
             SSP3_clim = SSP3_clim*(SSP3_g + total_climate_effect),
             SSP4_clim = SSP4_clim*(SSP4_g + total_climate_effect),
             SSP5_clim = SSP5_clim*(SSP5_g + total_climate_effect),
             year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
 
  
  save(done,file = here("data","temp","projections",paste0("full_SSP_gets_",v,".RData")))
  rm(done,i)
}
```



# BHM
## Load coefficients
```{r}
load(here("data","temp","BHM_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = BHM_model %>% coef(), Sigma = BHM_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  BHM_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r, eval= FALSE, purl = FALSE}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>%
  pivot_longer(cols = everything()) %>%
  ggplot(aes(x=value)) +
  geom_histogram() +
  facet_wrap(~name,scales = "free") +
  geom_vline(data = BHM_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>%
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```



## Collect Relevant Information
```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected
```




## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- ssp_ready %>% 
    filter(year==2011) %>% 
    inner_join(effect_standard %>% 
                 filter(year == 2011) %>% 
                 select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2012:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,ends_with("_clim")) %>% #contains(SSP_scenarios_running)
      
      inner_join(ssp_ready %>% 
                   select(-ends_with("_clim")) %>% 
                   filter(year == i-1), by = c("iso","year")) %>% 
      # this step: 
      inner_join(effect_standard %>% 
                   filter(year == i-1) %>% 
                   mutate(realisation = v) %>% 
                   select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      
      mutate(SSP1_clim = SSP1_clim*(SSP1_g + total_climate_effect),
             SSP2_clim = SSP2_clim*(SSP2_g + total_climate_effect),
             SSP3_clim = SSP3_clim*(SSP3_g + total_climate_effect),
             SSP4_clim = SSP4_clim*(SSP4_g + total_climate_effect),
             SSP5_clim = SSP5_clim*(SSP5_g + total_climate_effect),
             year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
  save(done,file = here("data","temp","projections",paste0("full_SSP_BHM_",v,".RData")))
  rm(done,i)
}
```



# LASSO
## Load coefficients
```{r}
load(here("data","temp","standard_lasso_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = lasso_standard_model %>% coef(), Sigma = lasso_standard_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  lasso_standard_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r, eval= FALSE, purl = FALSE}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>%
  pivot_longer(cols = everything()) %>%
  ggplot(aes(x=value)) +
  geom_histogram() +
  facet_wrap(~name,scales = "free") +
  geom_vline(data = lasso_standard_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>%
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```



## Collect Relevant Information
```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected
```




## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
library(doMC)
registerDoMC(if(coefsamples < detectCores()){coefsamples} else {detectCores()-1})  # coefsamples if enough cores available - otherwise total-1
foreach(v=1:coefsamples,.packages = loadedNamespaces()) %dopar% {
  #for (v in 1:coefsamples){
  print(v)
  
  # Calculate the climate effect
  effect_standard <- climate_subset
  for(var in climate_vars){
    #print(var)
    climate_subset %>% 
      select(all_of(var)) %>% 
      pull %>% "*"(selection_coefs_standard %>% 
                     slice(v) %>% 
                     select(all_of(paste0(var,"_coef"))) %>% 
                     pull) %>%
      as_tibble %>% 
      rename_all(~paste0(var,"_effect"))  %>% 
      bind_cols(effect_standard,.) -> effect_standard
  }
  
  done <- ssp_ready %>% 
    filter(year==2011) %>% 
    inner_join(effect_standard %>% 
                 filter(year == 2011) %>% 
                 select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
    mutate(realisation = v) %>% 
    relocate(c(realisation,final_temp), .after = year)
  
  for(i in 2012:2099){
    print(paste0("Realisation ",v," Year: ",i))
    done %>% 
      filter(year == i-1) %>% 
      select(iso, year, realisation, final_temp,ends_with("_clim")) %>% #contains(SSP_scenarios_running)
      
      inner_join(ssp_ready %>% 
                   select(-ends_with("_clim")) %>% 
                   filter(year == i-1), by = c("iso","year")) %>% 
      # this step: 
      inner_join(effect_standard %>% 
                   filter(year == i-1) %>% 
                   mutate(realisation = v) %>% 
                   select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
      mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
      
      mutate(SSP1_clim = SSP1_clim*(SSP1_g + total_climate_effect),
             SSP2_clim = SSP2_clim*(SSP2_g + total_climate_effect),
             SSP3_clim = SSP3_clim*(SSP3_g + total_climate_effect),
             SSP4_clim = SSP4_clim*(SSP4_g + total_climate_effect),
             SSP5_clim = SSP5_clim*(SSP5_g + total_climate_effect),
             year = i) %>% 
      bind_rows(done,.) -> done
    
  }
  
  
  save(done,file = here("data","temp","projections",paste0("full_SSP_LASSO_",v,".RData")))
  rm(done,i)
}
```

