---
title: "Country-Level Analysis"
author: "Moritz Schwarz and Felix Pretis"
version: "October 2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("output")) })
---

```{r,purl = FALSE}
knitr::opts_chunk$set(message = F,echo = T,fig.width = 10)
```


```{r "setup", message=FALSE}
library(tidyverse)
library(data.table)
library(gets)
library(here)
library(vroom)
library(MASS)

library(quantreg)

library(extrafont)
library(RColorBrewer)
library(Cairo)
library(viridis)

library(cowplot)
library(ggalt)
library(ggnewscale)


rm(list = ls())
select <- dplyr::select
```

What do I need for each country: 

- The 66%, 90% and 95% span for each country (rq regression)
- The Mean and the Median (rq regression)
- The marginal step (based on the rq regression)


# Calculate all Quantiles
```{r}
for(cubic in c(FALSE,TRUE)){
  files  <- list.files(here("data","out"),pattern = "EOC",full.names = T)
  #files <- grep("BMS",files,value=T,ignore.case = FALSE)
  
  overall_df <- tibble()
  for(i in 1:length(files)){
    #for(i in c(6,18)){
    print(list.files(here("data", "out"), pattern = "EOC")[i])
    load(files[i])
    
    tibble(name = gsub("_massive_EOC", "",
                       gsub(".RData", "", list.files(here("data", "out"), pattern = "EOC")[i], fixed = T))) %>%
      mutate(name = case_when(name=="Mueller_interaction_log_selected_restricted"~"Mueller_gets_RestrAdapt",
                              name=="Mueller_interaction_log_selected_unrestricted"~"Mueller_gets_URestrAdapt",
                              name=="Mueller_interaction_log_selected_altrestr1"~"Mueller_gets_AltRestr1",
                              name=="Mueller_interaction_log_selected_altrestr2"~"Mueller_gets_AltRestr2",
                              name=="Mueller_lasso_interaction_log_selected_altrestr1"~"Mueller_lasso_AltRestr1",
                              name=="Mueller_lasso_interaction_log_selected_altrestr2"~"Mueller_lasso_AltRestr2",
                              
                              name=="SSP_interaction_log_selected_restricted"~"SSP_gets_RestrAdapt",
                              name=="SSP_interaction_log_selected_unrestricted"~"SSP_gets_URestrAdapt",
                              name=="SSP_interaction_log_selected_altrestr1"~"SSP_gets_AltRestr1",
                              name=="SSP_interaction_log_selected_altrestr2"~"SSP_gets_AltRestr2",
                              name=="SSP_lasso_interaction_log_selected_altrestr1"~"SSP_lasso_AltRestr1",
                              name=="SSP_lasso_interaction_log_selected_altrestr2"~"SSP_lasso_AltRestr2",
                              TRUE~name)) %>% 
      separate(name, sep = "_", into = c("baseline", "model","spec"),fill = "right") -> name_df
    
    baseline <- name_df$baseline
    model <- name_df$model
    specification <- ifelse(is.na(name_df$spec),"standard",name_df$spec)
    
    
    if(model=="firstgets"){
      model <- "gets"
      specification <- "first"
    }
    if(model=="lastgets"){
      model <- "gets"
      specification <- "last"
    }
    if(model=="firstlasso"){
      model <- "lasso"
      specification <- "first"
    }
    if(model=="lastlasso"){
      model <- "lasso"
      specification <- "last"
    }
    
    #success <- FALSE
    massive_overall %>% distinct(final_temp) -> temperature_axis
    
    
    
    if(baseline == "Mueller"){
      
      
      if(grepl("BMS",files[i])){
        massive_overall %>% 
          group_by(iso,final_temp) %>% 
          summarise(diff = weighted.mean(diff,PMP_Exact),.groups="drop") -> massive_overall
      }
      form <- "diff ~ final_temp + I(final_temp*final_temp)"
      if(cubic){form <- paste0(form," + I(final_temp*final_temp*final_temp)")}
      form <- as.formula(form)
      
      
      
      for(country in unique(massive_overall$iso)){
        success <- FALSE
        while (!success) {
          try({
            print(country)
            intermed <- massive_overall %>% filter(iso==country)
            
            vlow <- rq(formula = form, data = intermed,method = "pfn",tau = 0.025)
            low <- rq(formula = form, data = intermed,method = "pfn",tau = 0.05)
            midl <- rq(formula = form, data = intermed,method = "pfn",tau = 0.25)
            med <- rq(formula = form, data = intermed,method = "pfn",tau = 0.5)
            midh <- rq(formula = form, data = intermed,method = "pfn",tau = 0.75)
            high <- rq(formula = form, data = intermed,method = "pfn",tau = 0.95)
            vhigh <- rq(formula = form, data = intermed,method = "pfn",tau = 0.975)
            
            
            tibble(
              final_temp = temperature_axis$final_temp,
              baseline = baseline,
              model = model,
              specification = specification,
              scenario = "Hundred",
              iso = country,
              vlow  = predict(vlow, newdata = temperature_axis),
              low  =  predict(low, newdata = temperature_axis),
              midl  = predict(midl, newdata = temperature_axis),
              med  =  predict(med, newdata = temperature_axis),
              midh  = predict(midh, newdata = temperature_axis),
              high  = predict(high, newdata = temperature_axis),
              vhigh = predict(vhigh, newdata = temperature_axis)
            ) %>% 
              bind_rows(overall_df, .) -> overall_df
            success <- TRUE
          },silent = FALSE)
        }
      }
      
      
    } else if (baseline == "SSP") {
      
      if(grepl("BMS",files[i])){
        massive_overall %>% 
          group_by(iso,final_temp) %>% 
          summarise(diff_SSP1 = weighted.mean(diff_SSP1,PMP_Exact),
                    diff_SSP2 = weighted.mean(diff_SSP2,PMP_Exact),
                    diff_SSP3 = weighted.mean(diff_SSP3,PMP_Exact),
                    diff_SSP4 = weighted.mean(diff_SSP4,PMP_Exact),
                    diff_SSP5 = weighted.mean(diff_SSP5,PMP_Exact),.groups="drop") -> massive_overall
      }
      
      for (scen in 1:5){
        print(paste0("SSP ",scen))
        
        for(country in unique(massive_overall$iso)){
          print(country)
          success <- FALSE
          intermed <- massive_overall %>% filter(iso==country)
          while(!success){
            try({
              form <- paste0("diff_SSP",scen," ~ final_temp + I(final_temp*final_temp)")
              if(cubic){form <- paste0(form," + I(final_temp*final_temp*final_temp)")}
              form <- as.formula(form)
              
              vlow <- rq(formula = form, data = intermed,method = "pfn",tau = 0.025)
              low <- rq(formula = form, data = intermed,method = "pfn",tau = 0.05)
              midl <- rq(formula = form, data = intermed,method = "pfn",tau = 0.25)
              med <- rq(formula = form, data = intermed,method = "pfn",tau = 0.5)
              midh <- rq(formula = form, data = intermed,method = "pfn",tau = 0.75)
              high <- rq(formula = form, data = intermed,method = "pfn",tau = 0.95)
              vhigh <- rq(formula = form, data = intermed,method = "pfn",tau = 0.975)
              
              
              tibble(
                final_temp = temperature_axis$final_temp,
                baseline = baseline,
                model = model,
                specification = specification,
                scenario = as.character(scen),
                iso=country,
                vlow  = predict(vlow, newdata = temperature_axis),
                low  =  predict(low, newdata = temperature_axis),
                midl  = predict(midl, newdata = temperature_axis),
                med  =  predict(med, newdata = temperature_axis),
                midh  = predict(midh, newdata = temperature_axis),
                high  = predict(high, newdata = temperature_axis),
                vhigh = predict(vhigh, newdata = temperature_axis)
              ) %>%
                bind_rows(overall_df, .) -> overall_df
              
              success <- TRUE
              
            },silent = FALSE)
          }
        }
      }
    }
    rm(vlow,low,midh,midl,med,high,vhigh)
  }
  
  overall_df %>% 
    arrange(baseline,model,specification,scenario,final_temp) -> overall_df
  
  write_csv(overall_df,here("data","out",paste0("all_models_iso_quantiles_",if(cubic){"cub"}else{"sq"},".csv")))
}

```



# Load data

```{r}
overall_df <- vroom(here("data","out","all_models_iso_quantiles_sq.csv"))
```

Renaming and preparing
```{r}
overall_df %>% 
  mutate(baseline = case_when(baseline=="Mueller"~"MSW",
                              TRUE~baseline)) %>% 
  mutate(across(c(where(is.double),-final_temp),~.-1)) %>% 
  rename(pc.025 = vlow,
         pc.05 = low,
         pc.25 = midl,
         pc.5 = med,
         pc.75 = midh,
         pc.95 = high,
         pc.975 = vhigh) -> df
```

Significance levels for all country estimates
```{r, eval=FALSE}
df %>% 
  mutate(sig.50 = ifelse(sign(pc.75)==sign(pc.25),1,0),
         sig.90 = ifelse(sign(pc.95)==sign(pc.05),1,0),
         sig.95 = ifelse(sign(pc.975)==sign(pc.025),1,0)) -> significance_all
```

figure out in which map the value is showing up (Map Position)
```{r}
df %>% 
  mutate(map_position = round(final_temp),
         map_position = ifelse(final_temp < 1.75,1,map_position)) %>% 
  
  # average over the map position
  group_by(baseline,model,specification,scenario,map_position,iso) %>% 
  summarise(across(where(is.numeric),.fns = mean),.groups = "drop") %>% 
  mutate(sig.50 = ifelse(sign(pc.75)==sign(pc.25),1,0),
         sig.90 = ifelse(sign(pc.95)==sign(pc.05),1,0),
         sig.95 = ifelse(sign(pc.975)==sign(pc.025),1,0)) %>% 
  select(-starts_with("pc."),pc.5) %>% 
  
  # Joining on the iso codes
  mutate(region = countrycode::countrycode(sourcevar = iso,origin = "iso3c",destination = "country.name")) %>% 
  relocate(region, .after = iso) %>% 
  mutate(region = case_when(region=="Myanmar (Burma)"~"Myanmar",
                            region=="Bosnia & Herzegovina"~"Bosnia and Herzegovina",
                            region=="Congo - Brazzaville"~"Republic of Congo",
                            region=="Congo - Kinshasa"~"Democratic Republic of the Congo",
                            TRUE~region)) -> map_values
```


```{r}
map_data("world") %>% 
  filter(!region=="Antarctica") %>% 
  mutate(region = case_when(region=="USA"~"United States",
                            region=="UK"~"United Kingdom",
                            region=="Czech Republic"~"Czechia",
                            region=="Ivory Coast"~"Côte d’Ivoire",
                            TRUE~region)) -> world_df

```


# Maps

## Manual: gets and LASSO combined 

Main Figure for PNAS Submission Oct 2020
<2°C 
3.5°C 
4.5°C

```{r}
world_df %>% 
  full_join(df %>% 
              mutate(map_position = NA,
                     map_position = case_when(final_temp < 2~"Below 2°C",
                                              final_temp>=3&final_temp<4~"3.5°C",
                                              final_temp>=4.5~">4.5°C")) %>% 
              
              # average over the map position
              group_by(baseline,model,specification,scenario,map_position,iso) %>% 
              summarise(across(where(is.numeric),.fns = mean),.groups = "drop") %>% 
              mutate(sig.50 = ifelse(sign(pc.75)==sign(pc.25),1,0),
                     sig.90 = ifelse(sign(pc.95)==sign(pc.05),1,0),
                     sig.95 = ifelse(sign(pc.975)==sign(pc.025),1,0)) %>% 
              select(-starts_with("pc."),pc.5) %>% 
              
              # Joining on the iso codes
              mutate(region = countrycode::countrycode(sourcevar = iso,origin = "iso3c",destination = "country.name")) %>% 
              relocate(region, .after = iso) %>% 
              mutate(region = case_when(region=="Myanmar (Burma)"~"Myanmar",
                                        region=="Bosnia & Herzegovina"~"Bosnia and Herzegovina",
                                        region=="Congo - Brazzaville"~"Republic of Congo",
                                        region=="Congo - Kinshasa"~"Democratic Republic of the Congo",
                                        TRUE~region))  %>%
              filter(baseline=="MSW",
                     specification=="standard",
                     model %in% c("LASSO","gets")),by="region") %>% 
  # if 90% not significant, then NA
  mutate(pc.5 = ifelse(sig.90 != 1, NA, pc.5)) -> intermed

intermed %>% 
  filter(!is.na(map_position)) %>% 
  mutate(map_position = factor(map_position,levels = c("Below 2°C","3.5°C",">4.5°C"))) %>% 
  ggplot() +
  facet_grid(map_position~model)+
  geom_polygon(aes(x=long,y=lat,group=group),fill="grey",inherit.aes = FALSE,data = world_df)+
  geom_polygon(aes(x=long,y=lat,group=group,fill=pc.5)) +
  coord_proj("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs") +
  
  
  #coord_quickmap()+
  scale_fill_gradientn(colours = brewer.pal(name = "RdBu",n=11), 
                       breaks = seq(from = -1, to = 1, by = 0.2),
                       guide = guide_colourbar(title = "Level Percentage Difference to baseline",
                                               title.position = "top"),
                       labels=c(as.character(scales::percent(seq(from = -1, to = 0.8, by = 0.2))),">100%"),
                       limits=c(-1,1),
                       oob=scales::squish,
                       na.value = "grey") +
  labs(x=NULL,y=NULL)+
  
  theme(legend.position = "bottom",
        panel.background = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "grey",fill=NA),
        text = element_text(family = "Georgia"),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        legend.key.size = unit(0.25, "cm"),
        legend.key.width = unit(1.5,"cm"),
        legend.text = element_text(family = "Georgia",size=8)) +
        ggsave(filename = here("output","figures","Map_MSW_getsLASSO_standard.jpg"),height = 6,width = 6)


```



## Loop

```{r}
set_null_device("png")
for(m in unique(map_values$baseline)){
  if(is.na(m)){next}
  for(k in unique(map_values$scenario)){
    if(is.na(k)){next}
    if(m=="MSW"&k %in% c(1:5)){next}
    if(m=="SSP"& k == "Hundred"){next}
    for(j in unique(map_values$specification)){
      if(is.na(j)){next}
      
      world_df %>% 
        full_join(map_values %>% 
                    filter(baseline==m,
                           scenario==k,
                           specification==j),by="region") %>% 
        # if 90% not significant, then NA
        mutate(pc.5 = ifelse(sig.90 != 1, NA, pc.5)) -> intermed
      
      
      
      for(n in unique(intermed$model)){
        if(is.na(n)){next}
        for(i in unique(map_values$map_position)){
          if(is.na(i)){next}
          
          
          
          print(paste(m,k,j,i,n,sep=" "))
          
          intermed %>% 
            filter(model==n|is.na(model)) %>% 
            
            filter(map_position==i|is.na(map_position)) %>% 
            
            ggplot() +
            #geom_polygon(data = map_data("world") %>%  filter(region !="Antarctica"),
            #             aes(x=long,y=lat,group=group),fill="white",color="black",inherit.aes = FALSE,size=0.1)+
            geom_polygon(aes(x=long,y=lat,group=group,fill=pc.5)) +
            coord_proj("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs") +
            
            #facet_wrap(~map_position)+
            #coord_quickmap()+
            scale_fill_gradientn(colours = brewer.pal(name = "RdBu",n=11), 
                                 breaks = seq(from = -1, to = 1, by = 0.2),
                                 guide = guide_colourbar(title = paste0("Level Percentage Difference to Baseline (",
                                                                        m," - ",k,")"),
                                                         title.position = "top"),
                                 labels=c(as.character(scales::percent(seq(from = -1, to = 0.8, by = 0.2))),">100%"),
                                 limits=c(-1,1),
                                 oob=scales::squish,
                                 na.value = "grey") +
            labs(x=NULL,y=NULL)+
            
            theme(legend.position = "bottom",
                  panel.background = element_blank(),
                  text = element_text(family = "Georgia"),
                  axis.ticks = element_blank(),
                  axis.text = element_blank()) -> plot
          
          #assign(x = paste("plot",i,j,k,m,sep = "_"),value = plot)
          assign(x = paste("plot",i,sep = "_"),value = plot)
          
          # 
          # theme(
          #   legend.position = "bottom",
          #   legend.key.size = unit(0.5, "cm"),
          #   legend.key.width = unit(3,"cm"),
          #   panel.spacing.x = unit(0.5, "lines"),
          #   axis.title = element_blank(),
          #   axis.text = element_blank(),
          #   axis.ticks = element_blank(),
          #   panel.background = element_blank(),
          #   strip.background = element_blank(),
          #   text = element_text(family = "Georgia"),
          #   plot.title = element_text(size = 15, margin = margin(b = 10),hjust = 0),
          #   plot.subtitle = element_text(size = 12, color = "darkslategrey", margin = margin(b = 25)),
          #   plot.caption = element_text(size = 8, margin = margin(t = 10), color = "grey70", hjust = 0),
          #   plot.background = element_blank()) 
        }
        
        legend <- get_legend(plot_1 + theme(legend.box.margin = margin(0, b = 10, 0, 0),
                                            legend.key.size = unit(0.25, "cm"),
                                            legend.key.width = unit(1.5,"cm"),
                                            legend.text = element_text(family = "Georgia",size=8)))
        
        A <- plot_grid(plotlist = list(plot_1 + theme(legend.position = "none"),
                                       plot_2 + theme(legend.position = "none"), 
                                       plot_3 + theme(legend.position = "none"), 
                                       plot_4 + theme(legend.position = "none"), 
                                       plot_5 + theme(legend.position = "none"), 
                                       plot_6 + theme(legend.position = "none")),
                       nrow = 3,labels = c("1.5°C","2°C","3°C","4°C","5°C","6°C"),label_fontfamily = "Georgia")
        B <- plot_grid(A,legend,nrow=2,rel_heights = c(1,0.1))
        ggsave(filename = here("output","figures",paste0("Map_",m,"_",k,"_",j,"_",n,".jpg")),plot = B,height = 6,width = 6)
      }
    }
  }
}



# countries <- c("USA","IND","BGD","CHN","BRA","RUS")
# ggplot(test %>% filter(sig.90==1,iso %in% countries),aes(x=final_temp,color=iso)) + 
#   geom_line(aes(y=pc.50))
#ggsave(plot,filename = here("output","figures",paste0("Map_",model,".pdf")),device = cairo_pdf,height=8,width = 6)

```



## Loop Significance

```{r}
set_null_device("png")
for(m in unique(map_values$baseline)){
  if(is.na(m)){next}
  for(k in unique(map_values$scenario)){
    if(is.na(k)){next}
    if(m=="MSW"&k %in% c(1:5)){next}
    if(m=="SSP"& k == "Hundred"){next}
    for(j in unique(map_values$specification)){
      if(is.na(j)){next}
      
      # m="MSW"
      # k="Hundred"
      # j="standard"
      
      
      world_df %>% 
        full_join(map_values %>% 
                    filter(baseline==m,
                           scenario==k,
                           specification==j),by="region") %>% 
        
        # if 90% not significant, then NA
        mutate(pc.5 = case_when(sig.50 == 0~"50% Range includes 0",
                                sig.50 == 1 & sig.90 == 0 & pc.5>0~"50% Range > 0",
                                sig.50 == 1 & sig.90 == 0 & pc.5<0~"50% Range < 0",
                                sig.90 == 1 & sig.95== 0 & pc.5>0 ~"90% Range > 0",
                                sig.90 == 1 & sig.95== 0 & pc.5<0 ~"90% Range < 0",
                                sig.95 == 1 & pc.5>0 ~"95% Range > 0",
                                sig.95 == 1 & pc.5<0 ~"95% Range < 0"),
               
               
               # pc.5 = factor(pc.5,levels = c("95% Range > 0","90% Range > 0","50% Range > 0","50% Range includes 0","empty2",
               #                               "50% Range < 0","90% Range < 0","95% Range < 0"))) -> intermed 
               pc.5 = factor(pc.5,levels = c("95% Range > 0","90% Range > 0","50% Range > 0","50% Range includes 0",
                                             "50% Range < 0","90% Range < 0","95% Range < 0"))) -> intermed 
      
      
      
      for(n in unique(intermed$model)){
        if(is.na(n)){next}
        print(paste(m,k,j,n,sep=" "))
        for(i in unique(map_values$map_position)){
          if(is.na(i)){next}
          
          # n = "gets"
          # i = 1
          
          
          
          # cols <- rev(RColorBrewer::brewer.pal(7,"RdBu"))
          # cols <- c(cols[1:4],"white",cols[5:7])
          pal_rdbu <- scales::brewer_pal(palette = "RdBu")(7)
          
          intermed %>% 
            filter(model==n|is.na(model)) %>% 
            
            filter(map_position==i|is.na(map_position)) %>% 
            
            ggplot() +
            #geom_polygon(data = map_data("world") %>%  filter(region !="Antarctica"),
            #             aes(x=long,y=lat,group=group),fill="grey",color="black",inherit.aes = FALSE,size=0.1) +
            geom_polygon(aes(x=long,y=lat,group=group,fill=pc.5)) +
            coord_proj("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs") +
            
            #new_scale_fill() +
            
            scale_fill_manual( name = "No Effect", breaks = c("50% Range includes 0",NA),
                               values=c(NA,NA,NA,pal_rdbu[4],NA,NA,NA,"grey"),drop=FALSE,na.value="grey",labels = c("50% Range includes 0","No Data")) +
            new_scale_fill() +
            geom_polygon(aes(x=long,y=lat,group=group,fill=pc.5)) +
            scale_fill_manual(name = "Positive Effect", breaks = c("50% Range > 0","90% Range > 0","95% Range > 0"),
                              values=c(pal_rdbu[7:5],NA,NA,NA,NA),drop=FALSE)+
            
            new_scale_fill() +
            geom_polygon(aes(x=long,y=lat,group=group,fill=pc.5)) +
            scale_fill_manual(name = "Negative Effect", breaks = c("50% Range < 0","90% Range < 0","95% Range < 0"),
                              values=c(NA,NA,NA,NA,pal_rdbu[3:1]),drop=FALSE) +
            
            theme_void()+
            labs(x=NULL,y=NULL)+
            
            theme(legend.position = "bottom",
                  legend.direction = "vertical",
                  panel.background = element_blank(),
                  text = element_text(family = "Georgia"),
                  axis.ticks = element_blank(),
                  axis.text = element_blank()) -> plot
          
          
          
          #assign(x = paste("plot",i,j,k,m,sep = "_"),value = plot)
          assign(x = paste("plot",i,sep = "_"),value = plot)
          
          # 
          # theme(
          #   legend.position = "bottom",
          #   legend.key.size = unit(0.5, "cm"),
          #   legend.key.width = unit(3,"cm"),
          #   panel.spacing.x = unit(0.5, "lines"),
          #   axis.title = element_blank(),
          #   axis.text = element_blank(),
          #   axis.ticks = element_blank(),
          #   panel.background = element_blank(),
          #   strip.background = element_blank(),
          #   text = element_text(family = "Georgia"),
          #   plot.title = element_text(size = 15, margin = margin(b = 10),hjust = 0),
          #   plot.subtitle = element_text(size = 12, color = "darkslategrey", margin = margin(b = 25)),
          #   plot.caption = element_text(size = 8, margin = margin(t = 10), color = "grey70", hjust = 0),
          #   plot.background = element_blank()) 
        }
        
        legend <- get_legend(plot_1 + theme(legend.text = element_text(family = "Georgia",size=8),
                                            legend.box.margin = margin(0, b = 10, 0, 0)))
        
        A <- plot_grid(plotlist = list(plot_1 + theme(legend.position = "none"),
                                       plot_2 + theme(legend.position = "none"), 
                                       plot_3 + theme(legend.position = "none"), 
                                       plot_4 + theme(legend.position = "none"), 
                                       plot_5 + theme(legend.position = "none"), 
                                       plot_6 + theme(legend.position = "none")),
                       nrow = 3,labels = c("1.5°C","2°C","3°C","4°C","5°C","6°C"),label_fontfamily = "Georgia")
        B <- plot_grid(A,legend,nrow=2,rel_heights = c(1,0.2))
        ggsave(filename = here("output","figures",paste0("MapSig_",m,"_",k,"_",j,"_",n,".jpg")),plot = B,height = 6,width = 6)
      }
    }
  }
}



# countries <- c("USA","IND","BGD","CHN","BRA","RUS")
# ggplot(test %>% filter(sig.90==1,iso %in% countries),aes(x=final_temp,color=iso)) + 
#   geom_line(aes(y=pc.50))
#ggsave(plot,filename = here("output","figures",paste0("Map_",model,".pdf")),device = cairo_pdf,height=8,width = 6)

```
