---
title: "Mueller et al Projection"
subtitle: "Standard, Max GDP Restriction and Do-no-worse Restriction using Log Interactions"
author: "Moritz Schwarz and Felix Pretis"
version: "2 June 2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("output")) })
---

```{r,purl = FALSE}
knitr::opts_chunk$set(message = F,echo = T,fig.width = 10)
```


```{r "setup", message=FALSE}
library(tidyverse)
library(data.table)
library(gets)
library(here)
library(vroom)
library(MASS)

library(extrafont)
library(RColorBrewer)
library(Cairo)
library(viridis)


rm(list = ls())
select <- dplyr::select
```

# Load Mueller at el data
```{r}
mueller <- readxl::read_excel(here("data","raw","Predictive_ Distributions_by_Country.xlsx"),
                              skip = 6,col_names = c("iso","empty1","value_2017","empty2","fifty_mean","fifty_0.05",
                                                     "fifty_0.16","fifty_0.5","fifty_0.84","fifty_0.95", "empty3","hundred_mean","hundred_0.05",
                                                     "hundred_0.16","hundred_0.5","hundred_0.84","hundred_0.95", "empty4","unknown")) %>% select(-contains("empty"))

mueller_mean <- mueller %>% 
  select(iso, value_2017, contains("mean"))

mueller_mean %>% 
  mutate(year = 2017,
         gdp_cap = exp(value_2017),
         gdp_cap_fifty = gdp_cap,
         gdp_cap_fifty_climate = gdp_cap_fifty,
         gdp_cap_hundred = gdp_cap,
         gdp_cap_hundred_climate = gdp_cap_hundred,
         fifty_mean = (fifty_mean/100)+1,
         hundred_mean = (hundred_mean/100)+1,
         value_2017 = NULL,
         gdp_cap = NULL) %>% 
  select(iso,year,gdp_cap_fifty, gdp_cap_hundred,everything()) -> mueller_df
```

## Prepare the Max GDP Restriction
Here we identify the 2017 Level of GDP that will act as our restriction.
```{r}
base_gdp <- mueller_df %>% filter(year==2017) %>% 
  select(iso,gdp_cap_fifty,gdp_cap_hundred) %>% 
  rename(base_fifty = gdp_cap_fifty,
         base_hundred = gdp_cap_hundred)

restrict_max_gdp_int = TRUE
```

```{r}
coefsamples <- 1
```


# GETS
## Load coefficients
```{r}
load(here("data","temp","standard_gets_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = standard_model %>% coef(), Sigma = standard_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  standard_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


```{r, eval= FALSE, purl = FALSE}
# Set eval=TRUE to get a simple plot of the mean coefficient and the draws that were taken
selection_coefs_standard %>% 
  pivot_longer(cols = everything()) %>% 
  ggplot(aes(x=value)) + 
  geom_histogram() + 
  facet_wrap(~name,scales = "free") + 
  geom_vline(data = standard_model %>%
               coef %>%
               data.frame(variable = names(.),
                          coefficient = .,
                          row.names = NULL) %>%
               pivot_wider(names_from = "variable",values_from = "coefficient") %>%
               rename_all(~tolower(.)) %>%
               select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
               rename_all(~paste0(.,"_coef")) %>% pivot_longer(cols = everything()),aes(xintercept=value))

```


## Collect Relevant Information

```{r}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

# selection_coefs_interaction_all %>% 
#   names %>% 
#   gsub("_coef","",.) %>% 
#   grep("_int",.,value = TRUE) %>% 
#   gsub("_int","",.) %>% 
#   unique -> interaction_vars_all
# 
# selection_coefs_interaction_selected %>%
#   names %>%
#   gsub("_coef","",.) %>%
#   grep("_int",.,value = TRUE) %>%
#   gsub("_int","",.) %>%
#   unique -> interaction_vars_selected

```

## Load climate data
```{r}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```


## Project (Server)
```{r}
v=1
# Calculate the climate effect
effect_standard <- climate_subset
for(var in climate_vars){
  #print(var)
  climate_subset %>% 
    select(all_of(var)) %>% 
    pull %>% "*"(selection_coefs_standard %>% 
                   slice(v) %>% 
                   select(all_of(paste0(var,"_coef"))) %>% 
                   pull) %>%
    as_tibble %>% 
    rename_all(~paste0(var,"_effect"))  %>% 
    bind_cols(effect_standard,.) -> effect_standard
}

done <- mueller_df %>% 
  select(-contains("fifty")) %>% 
  filter(year==2017) %>% 
  left_join(effect_standard %>% 
              filter(year == 2017) %>% 
              select(-model,-ensemble,-rcp),by = c("iso","year")) %>% 
  mutate(realisation = v) %>% 
  relocate(c(realisation,final_temp), .after = year)

for(i in 2018:2099){
  print(paste0("Realisation ",v," Year: ",i))
  done %>% 
    filter(year == i-1) %>% 
    select(iso, year, realisation, final_temp,contains("hundred")) %>% 
    # this step: 
    left_join(effect_standard %>% 
                filter(year == i-1) %>% 
                mutate(realisation = v) %>% 
                select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
    mutate(total_climate_effect = rowSums(select(., ends_with("effect")))) %>% 
    mutate(#gdp_cap_fifty = gdp_cap_fifty*fifty_mean,
      gdp_cap_hundred = gdp_cap_hundred*hundred_mean,
      #gdp_cap_fifty_climate = gdp_cap_fifty_climate*(fifty_mean + total_climate_effect),
      gdp_cap_hundred_climate = gdp_cap_hundred_climate*(hundred_mean + total_climate_effect),
      year = i) %>% 
    bind_rows(done,.) -> done
  
}

done_standard <- done

```


# Adaptation GETS

## Load Coefficients

### Standard (for restriction)
```{r, purl=FALSE}
load(here("data","temp","standard_gets_model.RData"))
####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_standard <- MASS::mvrnorm(n = coefsamples, mu = standard_model %>% coef(), Sigma = standard_model %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

# If we are just using one coefsample, we simply use the mean estimate from the model
if(coefsamples==1){
  standard_model %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_standard
}
```


### Log Interaction All
```{r, purl=FALSE}
load(here("data","temp","log_interaction_model_all.RData"))

####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_interaction_all_log <- MASS::mvrnorm(n = coefsamples, mu = interaction_model_all_log %>% coef(), Sigma = interaction_model_all_log %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

if(coefsamples==1){
  interaction_model_all_log %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_interaction_all_log
}
```


### Log Interaction Selected
```{r, purl=FALSE}
load(here("data","temp","log_interaction_model_selected.RData"))

####simulate coefficients, draw them form joint normal distribution
set.seed(123)
selection_coefs_interaction_selected_log <- MASS::mvrnorm(n = coefsamples, mu = interaction_model_selected_log %>% coef(), Sigma = interaction_model_selected_log %>% vcov()) %>%
  {if (is.vector(.)) t(.) else .} %>%
  data.frame() %>%
  rename_all(~ tolower(.)) %>%
  select(-l1.diff.ln_gdp_cap, -starts_with(c("year", "iis", "time", "iso"))) %>%
  rename_all(~ paste0(., "_coef"))

if(coefsamples==1){
  interaction_model_selected_log %>%
    coef %>%
    data.frame(variable = names(.),
               coefficient = .,
               row.names = NULL) %>%
    pivot_wider(names_from = "variable",values_from = "coefficient") %>%
    rename_all(~tolower(.)) %>%
    select(-l1.diff.ln_gdp_cap,-starts_with(c("year","iis","time","iso"))) %>% 
    rename_all(~paste0(.,"_coef")) -> selection_coefs_interaction_selected_log
}
```


## Collect Relevant Information

```{r, purl=FALSE}
selection_coefs_standard %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  unique -> climate_vars

selection_coefs_standard %>% 
  names %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_lin

selection_coefs_standard %>% 
  names %>% 
  grep("_2",.,value = TRUE) %>% 
  gsub("_coef|_2","",.) %>% 
  unique -> climate_vars_sq

selection_coefs_interaction_all_log %>% 
  names %>% 
  gsub("_coef","",.) %>% 
  grep("_int",.,value = TRUE) %>% 
  gsub("_int","",.) %>% 
  unique -> interaction_vars_all

selection_coefs_interaction_selected_log %>%
  names %>%
  gsub("_coef","",.) %>%
  grep("_int",.,value = TRUE) %>%
  gsub("_int","",.) %>%
  unique -> interaction_vars_selected
```

## Load climate data
```{r, purl=FALSE}
climate <- vroom(here("data","temp","corrected_anomaly_climatedata.csv"))
climate %>% 
  select(model,rcp,ensemble,final_temp,iso,year,all_of(climate_vars_lin),
         all_of(paste0(climate_vars_sq,"_2"))) %>% 
  drop_na -> climate_subset
#mutate(across(.cols = climate_vars_sq,.fns = list(`2` = ~.^2))) -> climate_subset
rm(climate)
```
# Alternative Restriction 1: Baseline Restriction and Max GDP

Idea: Because we are only attenuating the effect of climate change, when the standard effect would suggest that GDP decreases, the Adaptation equivalent can only increase by a maximum of the baseline. 

Option 1: if country would lose, best could do is baseline. 
Combined: can do no worse than the no-adaptation baseline, but if the signs don't agree can't do better than baseline growth


```{r}
base_gdp_2017 <- mueller_df %>% select(iso,gdp_cap_hundred) %>% rename(base_value_2017 = gdp_cap_hundred)
max_overall_gdp <- max(base_gdp$base_fifty)
```

## Project (Server)
```{r, purl=FALSE}
v=1

effect_interaction_selected_log <- climate_subset
# Calculate the climate effect
for(var in climate_vars){
  #print(var)
  climate_subset %>% 
    select(all_of(var)) %>% 
    pull %>% "*"(selection_coefs_interaction_selected_log %>% 
                   slice(v) %>% 
                   select(all_of(paste0(var,"_coef"))) %>% 
                   pull) %>%
    as_tibble %>% 
    rename_all(~paste0(var,"_effect"))  %>% 
    bind_cols(effect_interaction_selected_log,.) -> effect_interaction_selected_log
}

for(var in interaction_vars_selected){
  effect_interaction_selected_log %>% 
    select(all_of(var)) %>% 
    pull %>% "*"(selection_coefs_interaction_selected_log %>% 
                   slice(v) %>% 
                   select(all_of(paste0(var,"_int_coef"))) %>% 
                   pull) %>%
    as_tibble %>% 
    rename_all(~paste0(var,"_int_effect"))  %>% 
    bind_cols(effect_interaction_selected_log,.) -> effect_interaction_selected_log
}

# Calculate the standard climate effect
effect_standard <- climate_subset
for(var in climate_vars){
  #print(var)
  climate_subset %>% 
    select(all_of(var)) %>% 
    pull %>% "*"(selection_coefs_standard %>% 
                   slice(v) %>% 
                   select(all_of(paste0(var,"_coef"))) %>% 
                   pull) %>%
    as_tibble %>% 
    rename_all(~paste0(var,"_effect"))  %>% 
    bind_cols(effect_standard,.) -> effect_standard
}

effect_standard %>% 
  rename_with(.cols = contains("effect"),.fn = ~gsub("effect","stdeffect",.)) -> effect_std

effect_interaction_selected_log %>% 
  rename_with(.cols = contains("effect"),.fn = ~gsub("effect","logeffect",.)) %>% 
  bind_cols(effect_std %>% select(contains("stdeffect"))) -> effect_int

done <- mueller_df %>% 
  select(-contains("fifty")) %>% 
  filter(year==2017) %>% 
  left_join(effect_int %>% 
              filter(year == 2017) %>% 
              select(-model,-ensemble),by = c("iso","year")) %>% 
  
  #drop_na %>% 
  mutate(realisation = v) %>% 
  relocate(c(realisation,final_temp), .after = year)

for(i in 2018:2099){
  print(paste0("Realisation ",v," Year: ",i))
  #i=2018
  
  done %>% 
    filter(year == i-1) %>% 
    select(iso, year, final_temp, realisation, contains(c("hundred")),-contains("base")) %>% 
    left_join(effect_int %>% 
                filter(year == i-1) %>% 
                mutate(realisation = v) %>% 
                select(-model,-ensemble,-rcp),by = c("iso","year","final_temp","realisation")) %>% 
    
    mutate(#gdp_cap_fifty = gdp_cap_fifty*fifty_mean,
      gdp_cap_hundred = gdp_cap_hundred*hundred_mean) %>% 
    
    mutate(total_stdeffect = rowSums(select(.,contains("stdeffect"))),
           
           total_climlogeffect = rowSums(select(.,contains("logeffect"),-contains("_int_"))),
           total_inteffect =  rowSums(select(.,contains("_int_logeffect")))) %>% 
    
    # max GDP Restriction
    mutate(interaction_effect_hundred = total_climlogeffect + total_inteffect*log( 
      
      ifelse(gdp_cap_hundred_climate>max_overall_gdp,
             max_overall_gdp,
             gdp_cap_hundred_climate))) %>%
    
    
    mutate(total_effect_this_year_hundred = ifelse(total_stdeffect > interaction_effect_hundred,
                                                   total_stdeffect,
                                                   interaction_effect_hundred))   %>% 
    
    
    # in words: if there is a sign difference, take take the smaller of the interaction or the base effect
    mutate(gdp_cap_hundred_climate = gdp_cap_hundred_climate* 
             ifelse(
               test = sign(total_stdeffect)==-1 & sign(interaction_effect_hundred)==1, # if sign between stdeffect != interaction 
               yes = ifelse(hundred_mean<(total_effect_this_year_hundred+1),hundred_mean,(total_effect_this_year_hundred+1)),
               no = hundred_mean + total_effect_this_year_hundred
             )
    ) %>% 
    
    mutate(year = i) %>% 
    
    bind_rows(done,.) -> done
  
}


done_adaptation <- done 

```


# Create Plot
## Standard
```{r}
set_null_device("png")
countries <- c("USA","IND","CHN","RUS")

done_standard %>% 
  select(iso,year,final_temp,contains("gdp_cap")) %>% 
  mutate(diff_hundred = (gdp_cap_hundred_climate - gdp_cap_hundred)/gdp_cap_hundred) %>% 
  
  pivot_longer(cols = contains(c("diff","gdp_cap")),names_to = "variable",values_to = "value") %>% 
  
  filter(variable == "diff_hundred",iso %in% countries) %>% 
  
  ggplot(aes(x=year,y=value,color=final_temp, group=final_temp)) +
  coord_cartesian(ylim = c(-1,2))+
  geom_line() + 
  geom_hline(aes(yintercept = 0),linetype=2)+
  geom_hline(aes(yintercept = -1))+
  
  facet_wrap(~iso,nrow=1,labeller = labeller(iso = c("CHN"="China","IND" = "India","RUS" = "Russia","USA" = "United States"))) + 
  
  scale_color_viridis_c(name="Temperature Anomaly",labels = function(x){paste0(x,"°C")},
                        guide = guide_colorbar(title.position = "top")) +
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(breaks = c(2025,2050,2075,2100))+
  
  labs(y="Impact to baseline",x=NULL)+
  #title = "Standard Model Projections",subtitle = "gets Model used.")+
  
  theme_minimal() + 
  theme(legend.position = "bottom",
        panel.border = element_rect(colour = "black",size=0.5,fill=NA),
        text = element_text(family = "Georgia",size = 10)) -> A


done_standard %>% 
  select(iso,year,final_temp,contains("gdp_cap")) %>%
  left_join(mueller_df %>% select(iso,gdp_cap_hundred) %>% rename(base_value_2017 = gdp_cap_hundred),by="iso") %>% 
  
  mutate(diff = (gdp_cap_hundred_climate - base_value_2017)/base_value_2017) %>% 
  
  pivot_longer(cols = contains(c("diff")),names_to = "variable",values_to = "value") %>% 
  
  filter(iso %in% countries) %>% 
  
  
  ggplot(data = ,aes(x=year,y=value,color=final_temp, group=final_temp)) +
  coord_cartesian(ylim = c(-1,4))+
  geom_line() + 
  geom_hline(aes(yintercept = 0),linetype=2)+
  geom_hline(aes(yintercept = -1))+
  
  facet_wrap(~iso,nrow=1) + 
  
  scale_color_viridis_c(name="Temperature Anomaly",labels = function(x){paste0(x,"°C")},
                        guide = guide_colorbar(title.position = "top")) +
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(breaks = c(2025,2050,2075,2100))+
  labs(y="Impact to 2017 Value (MSW)",x=NULL)+#,
  #title = "Standard Model Projections",subtitle = "gets Model used.")+
  
  theme_minimal() + 
  theme(legend.position = "bottom",
        panel.border = element_rect(colour = "black",size=0.5,fill=NA),
        text = element_text(family = "Georgia",size = 10)) -> B


leg <- get_legend(A + theme(legend.box.margin = margin(0, b = 10, 0, 0),
                            legend.key.size = unit(0.25, "cm"),
                            legend.key.width = unit(1.5,"cm")))

combined <- plot_grid(A + theme(legend.position = "none"),
                      B + theme(legend.position = "none",
                                strip.text = element_blank()),
                      leg,
                      nrow=3,rel_heights = c(1,1,0.2))

ggsave(plot = combined,filename = here("output","figures","TimeSeries_gets.jpg"),width = 6,height = 6,dpi = 300)
```

## Adaptation
```{r}
set_null_device("png")
countries <- c("USA","IND","CHN","RUS")

done_adaptation %>% 
  select(iso,year,final_temp,contains("gdp_cap")) %>% 
  mutate(diff_hundred = (gdp_cap_hundred_climate - gdp_cap_hundred)/gdp_cap_hundred) %>% 
  
  pivot_longer(cols = contains(c("diff","gdp_cap")),names_to = "variable",values_to = "value") %>% 
  
  filter(variable == "diff_hundred",iso %in% countries) %>% 
  
  ggplot(aes(x=year,y=value,color=final_temp, group=final_temp)) +
  coord_cartesian(ylim = c(-1,2))+
  geom_line() + 
  geom_hline(aes(yintercept = 0),linetype=2)+
  geom_hline(aes(yintercept = -1))+
  
  facet_wrap(~iso,nrow=1,labeller = labeller(iso = c("CHN"="China","IND" = "India","RUS" = "Russia","USA" = "United States"))) + 
  
  scale_color_viridis_c(name="Temperature Anomaly",labels = function(x){paste0(x,"°C")},
                        guide = guide_colorbar(title.position = "top")) +
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(breaks = c(2025,2050,2075,2100))+
  
  labs(y="Impact to baseline",x=NULL)+
  #title = "Standard Model Projections",subtitle = "gets Model used.")+
  
  theme_minimal() + 
  theme(legend.position = "bottom",
        panel.border = element_rect(colour = "black",size=0.5,fill=NA),
        text = element_text(family = "Georgia",size = 10)) -> A


done_adaptation %>% 
  select(iso,year,final_temp,contains("gdp_cap")) %>%
  left_join(mueller_df %>% select(iso,gdp_cap_hundred) %>% rename(base_value_2017 = gdp_cap_hundred),by="iso") %>% 
  
  mutate(diff = (gdp_cap_hundred_climate - base_value_2017)/base_value_2017) %>% 
  
  pivot_longer(cols = contains(c("diff")),names_to = "variable",values_to = "value") %>% 
  
  filter(iso %in% countries) %>% 
  
  
  ggplot(data = ,aes(x=year,y=value,color=final_temp, group=final_temp)) +
  coord_cartesian(ylim = c(-1,4))+
  geom_line() + 
  geom_hline(aes(yintercept = 0),linetype=2)+
  geom_hline(aes(yintercept = -1))+
  
  facet_wrap(~iso,nrow=1) + 
  
  scale_color_viridis_c(name="Temperature Anomaly",labels = function(x){paste0(x,"°C")},
                        guide = guide_colorbar(title.position = "top")) +
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(breaks = c(2025,2050,2075,2100))+
  labs(y="Impact to 2017 Value (MSW)",x=NULL)+#,
  #title = "Standard Model Projections",subtitle = "gets Model used.")+
  
  theme_minimal() + 
  theme(legend.position = "bottom",
        panel.border = element_rect(colour = "black",size=0.5,fill=NA),
        text = element_text(family = "Georgia",size = 10)) -> B


leg <- get_legend(A + theme(legend.box.margin = margin(0, b = 10, 0, 0),
                            legend.key.size = unit(0.25, "cm"),
                            legend.key.width = unit(1.5,"cm")))

combined <- plot_grid(A + theme(legend.position = "none"),
                      B + theme(legend.position = "none",
                                strip.text = element_blank()),
                      leg,
                      nrow=3,rel_heights = c(1,1,0.2))

ggsave(plot = combined,filename = here("output","figures","TimeSeries_gets_Adaptation.jpg"),width = 6,height = 6,dpi = 300)
```


<!-- ```{r} -->
<!-- scale_color_viridis_c("Temp Anomaly")+ -->
<!--   scale_y_continuous(labels = scales::percent) + -->
<!--   labs(y = "Value as % of Mueller at al Baseline",x="") +  -->
<!--   theme(panel.grid.major = element_line(color="grey",size=0.1), -->
<!--         panel.background = element_blank(), -->
<!--         text = element_text(family = "Georgia",size = 15)) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- done %>%  -->
<!--   select(iso,year,final_temp,contains("gdp_cap")) %>% -->
<!--   left_join(mueller_df %>% select(iso,gdp_cap_hundred) %>% rename(base_value_2017 = gdp_cap_hundred),by="iso") %>%  -->

<!--   mutate(diff = (gdp_cap_hundred_climate - base_value_2017)/base_value_2017) %>%  -->

<!--   pivot_longer(cols = contains(c("diff")),names_to = "variable",values_to = "value") %>%  -->

<!--   filter(iso %in% countries) %>%  -->


<!--   ggplot(data = ,aes(x=year,y=value,color=final_temp, group=final_temp)) + -->

<!--   geom_line() +  -->
<!--   geom_hline(aes(yintercept = 0),linetype=2)+ -->
<!--   geom_hline(aes(yintercept = -1))+ -->

<!--   facet_wrap(~iso, scales = "free") +  -->

<!--   scale_color_viridis_c(name="Temperature Anomlay") + -->
<!--   scale_y_continuous(labels = scales::percent)+ -->
<!--   labs(y="GDP per capita impact to 2017 Value (MSW)", -->
<!--        title = "Standard Model Projections",subtitle = "gets Model used.")+ -->

<!--   theme_minimal() +  -->
<!--   theme(legend.position = "bottom", -->
<!--         panel.border = element_rect(colour = "black",size=0.5,fill=NA), -->
<!--         text = element_text(family = "Georgia",size = 10)) -->

<!-- scale_color_viridis_c("Temp Anomaly")+ -->
<!--   scale_y_continuous(labels = scales::percent)+ -->

<!--   labs(y = "Value as % of 2017 Value",x="") +  -->

<!--   theme(panel.grid.major = element_line(color="grey",size=0.1), -->
<!--         panel.background = element_blank(), -->
<!--         text = element_text(family = "Georgia",size = 15)) -->
<!-- ``` -->


<!-- # Function Definition -->
<!-- ```{r, eval= FALSE, purl = FALSE} -->
<!-- baseline_graph <- function(data, subtitle = ""){ -->
<!--   data %>%  -->
<!--     select(iso,year,final_temp,contains("gdp_cap")) %>%  -->
<!--     mutate(diff_fifty = (gdp_cap_fifty_climate - gdp_cap_fifty)/gdp_cap_fifty, -->
<!--            diff_hundred = (gdp_cap_hundred_climate - gdp_cap_hundred)/gdp_cap_hundred) %>%  -->

<!--     pivot_longer(cols = contains(c("diff","gdp_cap")),names_to = "variable",values_to = "value") %>%  -->

<!--     filter(variable == "diff_hundred",iso %in% c("USA","IND","CHN","BGD","RUS", "BRA")) %>%  -->

<!--     drop_na %>%  -->

<!--     mutate(value = ifelse(value>10e20,10e20,value)) -> intermed -->

<!--   ggplot(data = intermed,aes(x=year,y=value,color=final_temp, group=final_temp)) + -->
<!--     geom_line() +  -->
<!--     geom_hline(aes(yintercept = 0),linetype=2)+ -->
<!--     geom_hline(aes(yintercept = -1))+ -->
<!--     facet_wrap(~iso, scales = "free") +  -->
<!--     scale_color_viridis_c("Temp Anomaly")+ -->
<!--     scale_y_continuous(labels = ifelse(max(intermed$value)>1000,scales::scientific,scales::percent)) + -->
<!--     labs(title = "Change to Baseline", subtitle = subtitle, -->
<!--          y = "Value as % of Mueller at al Baseline",x="") +  -->
<!--     theme(panel.grid.major = element_line(color="grey",size=0.1), -->
<!--           panel.background = element_blank(), -->
<!--           text = element_text(family = "Georgia",size = 15)) -->
<!-- } -->

<!-- base_gdp_2017 <- mueller_df %>% select(iso,gdp_cap_fifty) %>% rename(base_value_2017 = gdp_cap_fifty) -->
<!-- basevalue_graph <- function(data, subtitle = ""){ -->
<!--   data %>%  -->
<!--     select(iso,year,final_temp,contains("gdp_cap")) %>% -->
<!--     left_join(base_gdp_2017,by="iso") %>%  -->

<!--     mutate(diff_fifty = (gdp_cap_fifty_climate - base_value_2017)/base_value_2017, -->
<!--            diff_hundred = (gdp_cap_hundred_climate - base_value_2017)/base_value_2017) %>%  -->

<!--     pivot_longer(cols = contains(c("diff","gdp_cap")),names_to = "variable",values_to = "value") %>%  -->

<!--     filter(variable == "diff_fifty",iso %in% c("USA","IND","CHN","BGD","RUS", "BRA")) %>%  -->

<!--     drop_na %>%  -->

<!--     mutate(value = ifelse(value>10e20,10e20,value)) -> intermed -->

<!--   # Plot -->
<!--   ggplot(data = intermed,aes(x=year,y=value,color=final_temp, group=final_temp)) + -->

<!--     geom_line() +  -->
<!--     geom_hline(aes(yintercept = 0),linetype=2)+ -->
<!--     geom_hline(aes(yintercept = -1))+ -->

<!--     facet_wrap(~iso, scales = "free") +  -->

<!--     scale_color_viridis_c("Temp Anomaly")+ -->
<!--     scale_y_continuous(labels = ifelse(max(intermed$value)>1000,scales::scientific,scales::percent))+ -->

<!--     labs(title = "Change to 2017 Value", y = "Value as % of 2017 Value",x="",subtitle = subtitle) +  -->

<!--     theme(panel.grid.major = element_line(color="grey",size=0.1), -->
<!--           panel.background = element_blank(), -->
<!--           text = element_text(family = "Georgia",size = 15)) -->
<!-- } -->

<!-- damage_function_graph <- function(data,  -->
<!--                                   time_period_start = 2095,  -->
<!--                                   time_period_end = 2099,  -->
<!--                                   confidence_degree = 2,  -->
<!--                                   uncertainty_low = 0.05,  -->
<!--                                   uncertainty_high = 0.95,  -->
<!--                                   slope.val = 1.5){ -->


<!--   mean_slope <- (slope.val/1000) #1000 to make it K/1000 GtC and 3.667 to convert C to CO2 - aka /3667. Conversion rate is from https://www.ipcc.ch/pdf/special-reports/srccs/srccs_annex1.pdf Table AI.6 IPCC Special Report on Carbon dioxide Capture and Storage -->


<!--   data %>%  -->
<!--     select(iso,year,final_temp,contains("gdp_cap")) %>%  -->
<!--     mutate(diff_fifty = (gdp_cap_fifty_climate - gdp_cap_fifty)/gdp_cap_fifty, -->
<!--            diff_hundred = (gdp_cap_hundred_climate - gdp_cap_hundred)/gdp_cap_hundred) %>%  -->

<!--     pivot_longer(cols = contains(c("diff","gdp_cap")),names_to = "variable",values_to = "value") %>%  -->

<!--     filter(variable == "diff_hundred") %>%  #,iso %in% c("USA","IND","CHN","BGD","RUS", "BRA")) %>%  -->

<!--     drop_na %>%  -->

<!--     mutate(value = ifelse(value>10e20,10e20,value)) %>%  -->
<!--     filter(year %in% c(time_period_start : time_period_end)) %>%  -->
<!--     group_by(iso,final_temp) %>%  -->
<!--     summarise(value = mean(value)) -> intermed -->

<!--   rq_model_mid <- quantreg::rq(formula = value ~ final_temp + if(confidence_degree==2){final_temp + I(final_temp*final_temp)}else{splines::bs(final_temp,df=confidence_degree)},tau=0.5,method = "pfn",data=intermed) -->
<!--   rq_model_high <- quantreg::rq(formula = value ~ final_temp + if(confidence_degree==2){final_temp + I(final_temp*final_temp)}else{splines::bs(final_temp,df=confidence_degree)},tau=0.95,method = "pfn",data=intermed) -->
<!--   rq_model_low <- quantreg::rq(formula = value ~ final_temp + if(confidence_degree==2){final_temp + I(final_temp*final_temp)}else{splines::bs(final_temp,df=confidence_degree)},tau=0.05,method = "pfn",data=intermed) -->

<!--   # Add quantiles to data frame -->
<!--   intermed[["pc.975"]] <- predict(rq_model_high) -->
<!--   intermed[["pc.50"]] <- predict(rq_model_mid) -->
<!--   intermed[["pc.025"]] <- predict(rq_model_low) -->
<!--   intermed[["mean"]] <- intermed %>% group_by(final_temp) %>% mutate(mean = mean(value)) %>% ungroup %>% pull(mean) -->

<!--   intermed <- intermed[!duplicated(intermed[,"final_temp",]),] -->


<!--   ggplot(data = intermed,aes(x=final_temp)) + -->
<!--     geom_line(aes(y=pc.50)) + -->
<!--     geom_line(aes(y=mean),linetype = 3) + -->
<!--     geom_ribbon(aes(ymin=pc.025,ymax = pc.975),fill="blue",alpha=0.2)+ -->
<!--     geom_hline(aes(yintercept = 0),linetype=2)+ -->
<!--     geom_hline(aes(yintercept = -1))+ -->
<!--     #scale_color_viridis_c("Temp Anomaly")+ -->

<!--     scale_y_continuous(labels = ifelse(max(intermed$value)>1000,scales::scientific,scales::percent)) + -->
<!--     scale_x_continuous(labels = function(x) paste(x,"°C",sep=""),sec.axis = sec_axis(trans= ~./mean_slope,name = "Cumulative Emissions")) +  -->

<!--     labs(title = "Range of Country-Level GDP per capita Impacts", -->
<!--          subtitle = paste0("End-of-Century Projections (",time_period_start," - ",time_period_end,") of Median GDP per Capita Levels Difference to Baseline Projections.\nThe confidence interval represents ",scales::percent(uncertainty_high - uncertainty_low)," uncertainty range.\nProjections made using ",intermed %>% distinct(final_temp) %>% nrow," CMIP5 ensemble runs and drawing ",coefsamples," coefficient samples from the parameter estimates."),# (except BMA estimates, which were averaged over PIP).", -->
<!--          x="Global Temperature Anomaly to 1850 - 1900", -->
<!--          y="Country-Level GDP per capita\nPercentage Difference to Baseline") +  -->
<!--     theme(panel.grid.major = element_line(color="grey",size=0.1), -->
<!--           panel.background = element_blank(), -->
<!--           text = element_text(family = "Georgia",size = 12)) -->
<!-- } -->

<!-- ``` -->
